\cvsection{Work experience}

\begin{cventries}
	\cventry
		{Software developer \& mathematician}
		{Innovaciones Tecnológicas del Sur}
		{Granada}
		{August 2024 - today}
		{
			\begin{cvitems}
    		\item {Designed and developed a state-of-the-art \textbf{scoring system for a federated intelligence platform}, which aims to filter out unrealiable sensitive information. This system is written in Python, exposing itself as a REST API.}
    		\item {Handled operations related to such system —i.e. deployments, CI/CD, containerization, etc.— using a modern stack of Python (uv, etc.) }
			\end{cvitems}
		}
	\cventry
		{Software developer \& DevOps} % Job title
		{T-Systems Iberia - BMW} % Organization
		{Granada} % Location
		{October 2022 - August 2024} % Date(s)
		{
				\begin{cvitems} % Description(s) of tasks/responsibilities
						\item {Member of multiple teams at BMW's Smart Factory Life Planning international project — a state-of-the-art enterprise solution to virtualize factories and their ecosystem, making them fully interactive in a 3D environment using Nvidia's Omniverse.}
						\item {Designed and implemented a Python-based REST-API server for migrating a legacy system into SW8P.}
						\item {Implemented extensions Nvidia's Omniverse main renderer —USD explorer— with tasks related to user interface, user experience and engine behavior.}
						\item {Maintained a Rust library for Omniverse which acts as a resolver, integrating legacy backends into the Omniverse ecosystem.}
						\item {Designed and implemented CI/CD pipelines and containerization for several applications using Github Actions.}
						\item {Deployed backends to the Azure Kubernetes cluster using Helm, migrating from on premise servers.}
				\end{cvitems}
		}
\end{cventries}
