\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    \cventry
      {\inlinelink{http://github.com/Asmilex/Raytracing}{github.com/Asmilex/Raytracing}}
      {Real time raytracing accelerated by GPU}
      {Granada, Spain}
      {June 2021 - July 2022}
      {
        \begin{cvitems} % Description(s)
          \item {Thesis of the Bachelor's Degree in Computer Engineering and Mathematics. Research of how to simulate light in real time using raytracing.}
          \item {Implemented a Vulkan path tracing engine based on Monte Carlo integration using Nvidia DesignWorks' Nvpro-samples library. The engine is hardware accelerated on modern Nvidia's RTX GPUs. The project was inspired by Ray Tracing In One Weekend series}
          \item {Analyzed the quality of the image in terms of rendering time and noise of the reconstruction.}
          \item {Designed and implemented a CI/CD system to build and deploy the documentation of the thesis. Based on Github Actions and custom Docker container images.}
        \end{cvitems}
      }

    \cventry
      {\inlinelink{https://asmilex.github.io/DIU21/\#/}{asmilex.github.io/DIU21}}
      {CherryTrip - UX Case Study}
      {Granada, Spain}
      {March 2021 - May 2021}
      {
        \begin{cvitems} % Description(s)
          \item {Analyzed, designed and mocked up an application for traveling in Granada for the pandemic era }
          \item {Deployed the result to Github Pages}
          \item {Used Figma to design the mockups}
        \end{cvitems}
      }

    \cventry
      {\inlinelink{https://github.com/Asmilex/Crystalshot}{github.com/Asmilex/Crystalshot}}
      {Crystalshot}
      {Jaén, Spain}
      {June 2020}
      {
        \begin{cvitems} % Description(s)
          \item {A little arcade game about crystals made for a homemade gamejam.}
          \item {Developed using Unity. Multiplayer for up to 4 players.}
        \end{cvitems}
      }
\end{cventries}